Selection coefficients at the phylogenetic and population-genetic scale

### 2022-02-22 manuscript/include-figures.tex
Refactored call to main(). DFE with SIFT scores

\subsection{Site-specific mutation-selection codon models.} 
\begin{center}
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.D_tajima.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.D_tajima.scatter.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.H_fay_wu.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.H_fay_wu.scatter.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.fay_wu.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.fay_wu.scatter.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.tajima.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.tajima.scatter.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.watterson.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.watterson.scatter.pdf} \\
\end{center}
\section{Bos taurus}

\subsection{UGBT}

\subsubsection*{SFS for site-specific Mutation-Selection codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.MutSel.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.MutSel.normalize.pdf} 
\end{minipage}
\\ 
\section{Chlorocebus sabaeus}

\subsection{Zambia}

\subsubsection*{SFS for site-specific Mutation-Selection codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Zambia.MutSel.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Zambia.MutSel.normalize.pdf} 
\end{minipage}
\\ 
\section{Homo sapiens}

\subsection{AMR}

\subsubsection*{SFS for site-specific Mutation-Selection codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AMR.MutSel.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AMR.MutSel.normalize.pdf} 
\end{minipage}
\\

>>>>

\subsection{Site-specific mutation-selection codon models.} 
\begin{center}
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.MutSel.P(S<0).heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.MutSel.P(S=0).heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.MutSel.P(S>0).heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.MutSel.D_tajima.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.MutSel.H_fay_wu.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.MutSel.fay_wu.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.MutSel.tajima.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.MutSel.watterson.heatmap.pdf} \\
\end{center}
\subsection{Site-specific codon models.} 
\begin{center}
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.Omega.P(S<0).heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.Omega.P(S=0).heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.Omega.P(S>0).heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.Omega.D_tajima.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.Omega.H_fay_wu.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.Omega.fay_wu.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.Omega.tajima.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.Omega.watterson.heatmap.pdf} \\
\end{center}
\subsection{Sift score} 
\begin{center}
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.SIFT.P(S<0).heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.SIFT.P(S=0).heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.SIFT.P(S>0).heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.SIFT.D_tajima.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.SIFT.H_fay_wu.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.SIFT.fay_wu.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.SIFT.tajima.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.SIFT.watterson.heatmap.pdf} \\
\end{center}
\section{Bos taurus}

\subsection{IRBT}

\subsubsection*{Site-specific Mutation-Selection codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.MutSel.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.MutSel.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.MutSel.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.MutSel.histogram.pdf} 
\end{minipage}
\\ 
\subsubsection*{Site-specific codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.Omega.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.Omega.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.Omega.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.Omega.histogram.pdf} 
\end{minipage}
\\ 
\subsubsection*{SIFT score} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.SIFT.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.SIFT.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.SIFT.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.SIFT_vs_MutSel.pdf} 
\end{minipage}
\\ 
\subsection{UGBT}

\subsubsection*{Site-specific Mutation-Selection codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.MutSel.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.MutSel.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.MutSel.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.MutSel.histogram.pdf} 
\end{minipage}
\\ 
\subsubsection*{Site-specific codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.Omega.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.Omega.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.Omega.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.Omega.histogram.pdf} 
\end{minipage}
\\ 
\subsubsection*{SIFT score} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.SIFT.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.SIFT.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.SIFT.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.SIFT_vs_MutSel.pdf} 
\end{minipage}
\\ 
\section{Canis familiaris}

\subsection{Canis}

\subsubsection*{Site-specific Mutation-Selection codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.MutSel.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.MutSel.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.MutSel.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.MutSel.histogram.pdf} 
\end{minipage}
\\ 
\subsubsection*{Site-specific codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.Omega.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.Omega.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.Omega.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.Omega.histogram.pdf} 
\end{minipage}
\\ 
\subsubsection*{SIFT score} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.SIFT.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.SIFT.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.SIFT.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.SIFT_vs_MutSel.pdf} 
\end{minipage}
\\ 
\section{Capra hircus}

\subsection{AUCH}

\subsubsection*{Site-specific Mutation-Selection codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.MutSel.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.MutSel.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.MutSel.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.MutSel.histogram.pdf} 
\end{minipage}
\\ 
\subsubsection*{Site-specific codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.Omega.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.Omega.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.Omega.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.Omega.histogram.pdf} 
\end{minipage}
\\ 
\subsubsection*{SIFT score} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.SIFT.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.SIFT.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.SIFT.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.SIFT_vs_MutSel.pdf} 
\end{minipage}
\\ 
\subsection{FRCH}

\subsubsection*{Site-specific Mutation-Selection codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.MutSel.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.MutSel.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.MutSel.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.MutSel.histogram.pdf} 
\end{minipage}
\\ 
\subsubsection*{Site-specific codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.Omega.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.Omega.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.Omega.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.Omega.histogram.pdf} 
\end{minipage}
\\ 
\subsubsection*{SIFT score} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.SIFT.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.SIFT.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.SIFT.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.SIFT_vs_MutSel.pdf} 
\end{minipage}
\\ 
\subsection{IRCA}

\subsubsection*{Site-specific Mutation-Selection codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.MutSel.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.MutSel.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.MutSel.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.MutSel.histogram.pdf} 
\end{minipage}
\\ 
\subsubsection*{Site-specific codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.Omega.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.Omega.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.Omega.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.Omega.histogram.pdf} 
\end{minipage}
\\ 
\subsubsection*{SIFT score} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.SIFT.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.SIFT.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.SIFT.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.SIFT_vs_MutSel.pdf} 
\end{minipage}
\\ 
\subsection{IRCH}

\subsubsection*{Site-specific Mutation-Selection codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.MutSel.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.MutSel.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.MutSel.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.MutSel.histogram.pdf} 
\end{minipage}
\\ 
\subsubsection*{Site-specific codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.Omega.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.Omega.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.Omega.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.Omega.histogram.pdf} 
\end{minipage}
\\ 
\subsubsection*{SIFT score} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.SIFT.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.SIFT.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.SIFT.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.SIFT_vs_MutSel.pdf} 
\end{minipage}
\\ 
\subsection{ITCH}

\subsubsection*{Site-specific Mutation-Selection codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.MutSel.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.MutSel.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.MutSel.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.MutSel.histogram.pdf} 
\end{minipage}
\\ 
\subsubsection*{Site-specific codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.Omega.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.Omega.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.Omega.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.Omega.histogram.pdf} 
\end{minipage}
\\ 
\subsubsection*{SIFT score} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.SIFT.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.SIFT.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.SIFT.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.SIFT_vs_MutSel.pdf} 
\end{minipage}
\\ 
\subsection{MOCH}

\subsubsection*{Site-specific Mutation-Selection codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.MutSel.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.MutSel.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.MutSel.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.MutSel.histogram.pdf} 
\end{minipage}
\\ 
\subsubsection*{Site-specific codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.Omega.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.Omega.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.Omega.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.Omega.histogram.pdf} 
\end{minipage}
\\ 
\subsubsection*{SIFT score} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.SIFT.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.SIFT.normalize.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.SIFT.polyDFE_D.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.SIFT_vs_MutSel.pdf} 
\end{minipage}
\\ 
\section{Chlorocebus sabaeus}

\subsection{Barbados}
